Frozen Civil Conflicts

### 2023-12-14 paper.qmd
Notes

>>>>

## Skeleton

Bayesian probit model

Let $y_i \in \{ 0, 1 \}$ be abinary indicator

- Unit of analysis - civil conflict episodes

  - Contiguous years of active fighting according to the UCDP definition

  - Justification --- not interested in duration or predicting
    __when__ a conflict terminates

- X a matrix of control covariates

- T a binary treatment matrix consisting of 3 variables:

    1. External state support for rebels
    2. External state support for the government
    3. Interaction between previous two indicators to capture the
       differential effect of both sides receiving external state
       support.

- Let $y^\star$ be a latent dependent variable such that ... regression equation ... and $P(y_i = 1) = \Phi(...)$ where $\Phi(\cdot)$ is the standard normal CDF.

    Then $\delta_{k_i}$ is the vector of group varying treatment effects. $\gamma_{c_i}$ is a country specific intercept to capture heterogeneity

I place weakly information priors with hierarchical priors on $\delta$ and $\gamma$ in order to partially pool the estimators.

... prior equations ...
